Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-07-09 MUSES_vs_BYOD_solutions.tex
Filling and finishing @deantares tables. Closes #37

\begin{table}[ht]
\begin{footnotesize}
  \centering
  \renewcommand{\arraystretch}{2.0}% Spread rows out...
%  \resizebox{12cm}{!}{
  \begin{tabular}{>{\centering\bfseries}m{0.6in} >{\centering}m{0.6in} >{\centering}m{0.6in} >{\centering}m{0.6in} >{\centering}m{0.6in} >{\centering\arraybackslash}m{0.6in}}
    \toprule
      & \textbf{Offline threat detection method} & \textbf{Updatable database} & \textbf{Standalone} & \textbf{Non-invasive data access} & \textbf{Superuser system control} \\
    \midrule
    MUSES & \cmark & \cmark & \cmark & \cmark & \cmark  \\
     \arrayrulecolor[gray]{0.6}\hline
    IBM Mobile Security & \xmark & \xmark & \cmark & \xmark & \xmark  \\
     \arrayrulecolor[gray]{0.6}\hline
    Sophos Mobile Control & \cmark & \xmark & \cmark & \xmark & \xmark \\
     \arrayrulecolor[gray]{0.6}\hline
    Samsung Knox & \cmark & \nmark & \cmark & \nmark & \cmark\\
     \arrayrulecolor[gray]{0.6}\hline
     Blackbery Balance & \nmark & \nmark & \cmark & \nmark & \cmark\\
     \arrayrulecolor[gray]{0.6}\hline
    Blackphone & \nmark & \nmark & \cmark & \cmark & \nmark\\
     \arrayrulecolor[gray]{0.6}\hline
    Android for Work & \xmark & \xmark & \cmark & \xmark & \cmark\\
    \bottomrule
  \end{tabular}
%  }
\end{footnotesize}
  \caption{Features of the analyzed tools regarding the proposed taxonomy to classify BYOD systems (see Section \ref{sec:toolsreview}).}
  \label{tab:taxonomy}
\end{table}

\begin{table}[ht]
\begin{footnotesize}
  \centering
  \renewcommand{\arraystretch}{1.8}% Spread rows out...
%  \resizebox{8cm}{!}{
  \begin{tabular}{>{\centering\bfseries}m{1in} >{\centering}m{1in} >{\centering}m{1in} >{\centering\arraybackslash}m{1in}}
       \toprule
      & \textbf{License} & \textbf{Devices} & \textbf{Price} \\
       \midrule
    MUSES & OpenSource &  & Free  \\
       \arrayrulecolor[gray]{0.8}\hline
    IBM Mobile Security & Proprietary & IOS, Android, Windows Phone, Blackberry  &  By Request\\\\
        \arrayrulecolor[gray]{0.8}\hline
    Sophos Mobile Control & Proprietary & IOS, Android, Windows Phone  &  By Request\\
        \arrayrulecolor[gray]{0.8}\hline
    Samsung Knox and Blackbery Balance & Proprietary & Android Samsung Devices and IOS & 12\$ per year/device \\
        \arrayrulecolor[gray]{0.8}\hline
    Blackphone & Proprietary & Own device & 120\$ per year \\
        \arrayrulecolor[gray]{0.8}\hline
    Android for Work & Proprietary & Android and devices with Chrome Browser &  12\$ per month/user\\
       \bottomrule
  \end{tabular}
%  }
\end{footnotesize}
  \caption{Features of the analyzed products considering licenses, type of devices and price.}
  \label{tab:features}
\end{table}
% Antonio - Antares, ¿no había más tablas?
% Por favor, que alguien rellene los datos de la solución de IBM. ¿Fergu?¿Antares?
% Quizá habría que indicar que MUSES se puede instalar en PC también en la tabla. ¿Sabéis si los demás se puede o son sólo para smartphones/tablets?

>>>>

\begin{table}[ht]
\begin{footnotesize}
  \centering
  \renewcommand{\arraystretch}{2.0}% Spread rows out...
%  \resizebox{12cm}{!}{
  \begin{tabular}{>{\centering\bfseries}m{0.6in} >{\centering}m{0.6in} >{\centering}m{0.6in} >{\centering}m{0.6in} >{\centering}m{0.6in} >{\centering\arraybackslash}m{0.6in}}
    \toprule
      & \textbf{Offline threat detection method} & \textbf{Updatable database} & \textbf{Standalone} & \textbf{Non-invasive data access} & \textbf{Superuser system control} \\
    \midrule
    MUSES & \cmark & \cmark & \cmark & \cmark & \cmark  \\
     \arrayrulecolor[gray]{0.6}\hline
    IBM Mobile Security & \xmark & \xmark & \cmark & \xmark & \xmark  \\
     \arrayrulecolor[gray]{0.6}\hline
    Sophos Mobile Control & \cmark & \xmark & \cmark & \xmark & \xmark \\
     \arrayrulecolor[gray]{0.6}\hline
    Samsung Knox & \cmark & \xmark & \cmark & \cmark & \cmark\\
     \arrayrulecolor[gray]{0.6}\hline
     Blackbery Balance & \xmark & \xmark & \cmark & \cmark & \cmark\\
     \arrayrulecolor[gray]{0.6}\hline
    Blackphone & \nmark & \nmark & \cmark & \cmark & \cmark\\
     \arrayrulecolor[gray]{0.6}\hline
    Android for Work & \cmark & \xmark & \cmark & \cmark & \cmark\\
    \bottomrule
  \end{tabular}
%  }
\end{footnotesize}
  \caption{Features of the analyzed tools with regard to the proposed taxonomy to classify BYOD systems (see Section \ref{sec:toolsreview}).}
  \label{tab:taxonomy}
\end{table}

\begin{table}[ht]
\begin{footnotesize}
  \centering
  \renewcommand{\arraystretch}{1.8}% Spread rows out...
%  \resizebox{8cm}{!}{
  \begin{tabular}{>{\centering\bfseries}m{1in} >{\centering}m{1in} >{\centering}m{1in} >{\centering\arraybackslash}m{1in}}
       \toprule
      & \textbf{License} & \textbf{Devices} & \textbf{Price} \\
       \midrule
    MUSES & OpenSource & Android, Windows 8.1, Windows Phone, iOS & Free  \\
       \arrayrulecolor[gray]{0.8}\hline
    IBM Mobile Security & Proprietary & IOS, Android, Windows Phone, Blackberry  &  By Request\\\\
        \arrayrulecolor[gray]{0.8}\hline
    Sophos Mobile Control & Proprietary & IOS, Android, Windows Phone  &  By Request\\
        \arrayrulecolor[gray]{0.8}\hline
    Samsung Knox and Blackbery Balance & Proprietary & Android Samsung Devices and IOS & 12\$ per year/device \\
        \arrayrulecolor[gray]{0.8}\hline
    Blackphone & Proprietary & Own device & 120\$ per year \\
        \arrayrulecolor[gray]{0.8}\hline
    Android for Work & Proprietary & Android and devices with Chrome Browser &  12\$ per month/user\\
       \bottomrule
  \end{tabular}
%  }
\end{footnotesize}
  \caption{Features of the analyzed products considering licenses, type of devices and OS, and price.}
  \label{tab:features}
\end{table}
% Antonio - Antares, ¿no había más tablas?
% Por favor, que alguien rellene los datos de la solución de IBM. ¿Fergu?¿Antares?
% Quizá habría que indicar que MUSES se puede instalar en PC también en la tabla. ¿Sabéis si los demás se puede o son sólo para smartphones/tablets?
